### 2015-09-12 vmcai-2016-tex/intro.tex
Fixed some obvious dumbness

The contribution of this work is a symbolic initialization scheme for uninitialized pointers in a fully symbolic heap. Where GSE lazily instantiates uninitialized pointers to either reference NULL, a new instance of the correct type, or an alias to a previously initialized object, the symbolic initialization in this work creates a guarded value set expressing all of these eventualities in the same symbolic heap. Where GSE branches the search space on each choice, symbolic initialization does not. Symbolic initialization only branches on reference compares, partitioning the symbolic to indicate heaps where the references alias and heaps where the references do not.

This paper includes a proof that symbolic initialization is sound and complete with respect to properties provable by GSE. Such a results is important because it means that symbolic initialization can be used to create input heaps for other analyses in a way that is provably correct with regards to GSE: there are no missing heaps and there are no extra heaps.

>>>>

The contribution of this work is a symbolic initialization scheme for uninitialized pointers in a fully symbolic heap. Where GSE lazily instantiates uninitialized pointers to either reference NULL, a new instance of the correct type, or an alias to a previously initialized object, the symbolic initialization in this work creates a guarded value set expressing all of these eventualities in the same symbolic heap. Where GSE branches the search space on each choice, symbolic initialization does not. Symbolic initialization only branches on reference compares, partitioning the symbolic heap to indicate heaps where the references alias and heaps where the references do not.

This paper includes a proof that symbolic initialization is sound and complete with respect to properties provable by GSE. Such a result is important because it means that symbolic initialization can be used to create input heaps for other analyses in a way that is provably correct with regards to GSE: there are no missing heaps and there are no extra heaps.

### 2015-09-12 vmcai-2016-tex/summary-heap.tex
Fixed some obvious dumbness

The reference $\cfgnt{r}_\mathit{un}$ is a special reference to
indicate something that has yet to be initialized. In general,every
symbolic heap contains two special locations, null
($\cfgnt{l}_\mathit{null}$), and uninitialized
($\cfgnt{l}_\mathit{un}$), with corresponding references
$\cfgnt{r}_\mathit{null}$ and $\cfgnt{r}_\mathit{un}$ where
$\cfgnt{L}(\cfgnt{r}_\mathit{null}) =
\{(\cfgt{true}\ \cfgnt{l}_\mathit{null})\}$ and
$\cfgnt{L}(\cfgnt{r}_\mathit{un}) =
\{(\cfgt{true}\ \cfgnt{l}_\mathit{un})\}$.

@@

\input{surface-syntax}
\input{machine-syntax}
\begin{figure}[t]
\begin{center}
\begin{tabular}{c}
\scalebox{0.9}{\usebox{\boxSurface}} \\
(a) \\\\
\scalebox{0.9}{\usebox{\boxMachine}} \\
(b)
\end{tabular}
\end{center}
\caption{ (a) The surface syntax. (b) The machine syntax with $\bowtie\ \in \{\wedge,\vee,\Rightarrow\}$.}
\label{fig:syntax}
\end{figure}

@@

Given an input program $\lp\mu\ \lp\cfgnt{C}\ \cfgnt{m}\rp\rp$, the expression for the initial machine state is
$$
\begin{array}{l}
\lp\mu 
\ \cfgnt{L}[\cfgnt{r}_\mathit{null} \mapsto \{\lp\cfgt{true}\ \cfgnt{l}_\mathit{null})\}\rp] 
           [\cfgnt{r}_\mathit{un} \mapsto \{\lp\cfgt{true}\ \cfgnt{l}_\mathit{un}\rp\}] \\
\ \cfgnt{R}
\ \cfgt{true}\ \eta\  \lp\lp\cfgt{new}\ \cfgnt{C}\rp\ \cfgt{@}\ \cfgnt{m}\ \cfgt{true}\rp\rp\ \cfgt{end}\rp
\end{array}
$$
The semantics are expressed as
rewrites on strings using pattern matching. 
Consider the rewrite rule
for the beginning of a field access instruction:
$$
\mprset{flushleft}
	\inferrule[Field Access(eval)]{}{
      \lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \lp \cfgnt{e}\ \cfgt{\$}\ \cfgnt{f}\rp \ \cfgnt{k}\rp  \rcom 
      \lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \cfgnt{e}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp 
	}
$$
If the string representing the current state matches the left side, then it
creates the new string on the right. In this example, the new string
on the right is now evaluating the expression $\cfgnt{e}$ in the field
access, and it includes the continuation indicating that it still
needs to complete the actual field access once the expression is
evaluated.
%
%Other more complex rules, such as one to create a new instance of a
%class, define constraints on the rewrites and more complex
%transformations on the heap.
%$$
%\mprset{flushleft}
%	\inferrule[New]{
%      \cfgnt{r} = \mathrm{stack}_r\lp \rp\\
%      l = \mathrm{fresh}_l\lp \cfgnt{C}\rp\\\\
%      \cfgnt{R}^\prime = \cfgnt{R}[\forall \cfgnt{f} \in \mathit{fields}\lp \mathrm{C}\rp \ \lp \lp l\ \cfgnt{f}\rp  \mapsto \cfgnt{r}_\mathit{null} \rp ] \\\\
%      \cfgnt{L}^\prime = \cfgnt{L}[\cfgnt{r} \mapsto \{\lp \cfgt{true}\ l\rp \}]
%    }{
%      \lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \lp \cfgt{new}\ \cfgnt{C}\rp \ \cfgnt{k}\rp  \rcom
%      \lp \cfgnt{L}^\prime\ \cfgnt{R}^\prime\ \phi\ \eta\ \cfgnt{r}\ \cfgnt{k}\rp 
%	}
%$$ In this rule, when the string matches the new-expression, it is
%        rewritten to use a new heap location where all of the fields
%        for the new object point to $\cfgnt{r}_\mathit{null}$ and the
%        location map points a new stack reference to that new object.
%        New heap locations returned from $\mathrm{fresh}_l$ are monotonically
%        increasing.
%        Also note that references for objects from the new-expression are
%        auxiliary literals, so they do not appear in any constraint in
%        the symbolic heap as an aliasing option. 
%        
% \input{javalite-common}
%

>>>>

The reference $\cfgnt{r}_\mathit{un}$ is a special reference to
indicate something that has yet to be initialized. In general, every
symbolic heap contains two special locations, null
($\cfgnt{l}_\mathit{null}$), and uninitialized
($\cfgnt{l}_\mathit{un}$), with corresponding references
$\cfgnt{r}_\mathit{null}$ and $\cfgnt{r}_\mathit{un}$ where
$\cfgnt{L}(\cfgnt{r}_\mathit{null}) =
\{(\cfgt{true}\ \cfgnt{l}_\mathit{null})\}$ and
$\cfgnt{L}(\cfgnt{r}_\mathit{un}) =
\{(\cfgt{true}\ \cfgnt{l}_\mathit{un})\}$.

@@

\input{surface-syntax}
\input{machine-syntax}
\begin{figure}[t]
\begin{center}
\begin{tabular}{c}
\scalebox{0.9}{\usebox{\boxSurface}} \\
(a) \\\\
\scalebox{0.9}{\usebox{\boxMachine}} \\
(b)
\end{tabular}
\end{center}
\caption{ (a) The surface syntax. (b) The machine syntax.}
\label{fig:syntax}
\end{figure}

@@

\begin{comment}
Given an input program $\lp\mu\ \lp\cfgnt{C}\ \cfgnt{m}\rp\rp$, the expression for the initial machine state is
$$
\begin{array}{l}
\lp\mu 
\ \cfgnt{L}[\cfgnt{r}_\mathit{null} \mapsto \{\lp\cfgt{true}\ \cfgnt{l}_\mathit{null})\}\rp] 
           [\cfgnt{r}_\mathit{un} \mapsto \{\lp\cfgt{true}\ \cfgnt{l}_\mathit{un}\rp\}] \\
\ \cfgnt{R}
\ \cfgt{true}\ \eta\  \lp\lp\cfgt{new}\ \cfgnt{C}\rp\ \cfgt{@}\ \cfgnt{m}\ \cfgt{true}\rp\rp\ \cfgt{end}\rp
\end{array}
$$
\end{comment}

The semantics are expressed as
rewrites on strings using pattern matching. 
Consider the rewrite rule
for the beginning of a field access instruction:
$$
\mprset{flushleft}
	\inferrule[Field Access(eval)]{}{
      \lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \lp \cfgnt{e}\ \cfgt{\$}\ \cfgnt{f}\rp \ \cfgnt{k}\rp  \rcom 
      \lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \cfgnt{e}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp 
	}
$$
If the string representing the current state matches the left side, then it
creates the new string on the right. In this example, the new string
on the right is now evaluating the expression $\cfgnt{e}$ in the field
access, and it includes the continuation indicating that it still
needs to complete the actual field access once the expression is
evaluated.
%
%Other more complex rules, such as one to create a new instance of a
%class, define constraints on the rewrites and more complex
%transformations on the heap.
%$$
%\mprset{flushleft}
%	\inferrule[New]{
%      \cfgnt{r} = \mathrm{stack}_r\lp \rp\\
%      l = \mathrm{fresh}_l\lp \cfgnt{C}\rp\\\\
%      \cfgnt{R}^\prime = \cfgnt{R}[\forall \cfgnt{f} \in \mathit{fields}\lp \mathrm{C}\rp \ \lp \lp l\ \cfgnt{f}\rp  \mapsto \cfgnt{r}_\mathit{null} \rp ] \\\\
%      \cfgnt{L}^\prime = \cfgnt{L}[\cfgnt{r} \mapsto \{\lp \cfgt{true}\ l\rp \}]
%    }{
%      \lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \lp \cfgt{new}\ \cfgnt{C}\rp \ \cfgnt{k}\rp  \rcom
%      \lp \cfgnt{L}^\prime\ \cfgnt{R}^\prime\ \phi\ \eta\ \cfgnt{r}\ \cfgnt{k}\rp 
%	}
%$$ In this rule, when the string matches the new-expression, it is
%        rewritten to use a new heap location where all of the fields
%        for the new object point to $\cfgnt{r}_\mathit{null}$ and the
%        location map points a new stack reference to that new object.
%        New heap locations returned from $\mathrm{fresh}_l$ are monotonically
%        increasing.
%        Also note that references for objects from the new-expression are
%        auxiliary literals, so they do not appear in any constraint in
%        the symbolic heap as an aliasing option. 
%        
% \input{javalite-common}
%
